---
title: "business-logic"
output: html_document
date: "2023-02-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This script contains some business-logic function for the Shiny app. These functions will later be used inside the app's server code, but also within some modules.

For example, suppose we need to generate a bar plot that shows how many times certain characters appeared in a selected Harry Potter movie.
We need to load script data (we have some built-in package data) and then to generate a bar plot.

What to return?   ggplot

```{r character mentions}
# Helper function for data loading
load_and_manipulate_script_data <- function(data) {
  movie_script_data <- data
  colnames(movie_script_data) <- tolower(colnames(movie_script_data))
  return(movie_script_data)
}

# Load some built-in data
movie_script_data <- load_and_manipulate_script_data(myGolemApp::hp_movie_1)  # built-in data
# The built-in data was previously prepared. 
# The preparation code is in the data-raw/hp_movie_1.R script.

# Generate plot
ggplot2::ggplot(movie_script_data, ggplot2::aes(x = reorder(character,character,
                                           function(x)-length(x)))) +
        geom_bar(fill = "#14304d") +
        ggtitle(paste("How Many Times Each Character Spoke in the ", 
                      "Harry Potter and the Philosopher's Stone")) +
        xlab("Characters") + 
        ylab("Number of times mentioned") +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
              plot.title = element_text(hjust = 0.5))
```

Next, we have a dataset that contains some basic information about each of the characters that appear in the first three Harry Potter movies.
We need to select on of them, filter the table so that only information about that character remains in it, and, we also want to delet dots from
the column names (replace them with spaces). Also, we want to eliminate the id column from our table, because it's useless.

Steps:
  - load
  - filter
  - manipulate
  
What to return?   Resulting data frame (we expect it to have one row only - for one character)

```{r character exploration}
library(dplyr)
# load character data (built-in data)
characters_dataset <-  myGolemApp::characters

# Filter data such that the resulting data frame contains only the data
# for the selected character + exclude specified columns
filtered_data <- characters_dataset %>% 
  dplyr::filter(Name == "Hermione Jean Granger") %>% 
  dplyr::select(-"Id")

# Remove dots from column names
names(filtered_data) <- gsub("\\.", " ", names(filtered_data))

filtered_data
```
